\chapter{Jacobian Tests}

\section{Fluid-mass time derivative}

The following tests of the Jacobian are performed on the fluid-mass time derivative kernel (PorousFlowMassTimeDerivative).
\begin{enumerate}
\item single-phase, with a single component, with a van-Genuchten capillary pressure, constant bulk-modulus density and constant porosity.
\item single-phase, with 3 components, with a van-Genuchten capillary pressure, constant bulk-modulus density and constant porosity.
\item 2-phase PP formulation, with 2 components (that exist in both phases), with a van-Genuchten capillary pressure, constant bulk-modulus density for each phase and constant porosity.
\item 2-phase PP formulation, with 3 components (that exist in both phases), with a van-Genuchten capillary pressure, constant bulk-modulus density for each phase and constant porosity.
\end{enumerate}


\section{Fluid Advective Flux}

The following tests of the Jacobian are performed on the fluid-mass advective flux kernel (PorousFlowAdvectiveFlux).
\begin{enumerate}
\item single-phase, with 1 component, constant viscosity, constant insitu-permeability, density with constant bulk modulus, Corey relative permeability, nonzero gravity, with van-Genuchten capillary pressure.
\item single-phase, with 3 components, constant viscosity, constant insitu-permeability, density with constant bulk modulus, Corey relative permeability, nonzero gravity, with van-Genuchten capillary pressure.
\item 2-phase (PP formulation), with 2 components (that exist in both phases), constant viscosity for each phase, constant insitu-permeability, density with constant bulk modulus for each phase, Corey relative permeability for each phase, nonzero gravity, with van-Genuchten capillary pressure.
\item 2-phase (PP formulation), with 3 components (that exist in both phases), constant viscosity for each phase, constant insitu-permeability, density with constant bulk modulus for each phase, Corey relative permeability for each phase, nonzero gravity, with van-Genuchten capillary pressure.
\end{enumerate}
